---
title: "JRP Pilot 1 (UK data)"
author: "Jelka Stojanov"
date: "10/02/2022"
output: html_document
---

Load packages

```{r}
library(interactions)
library(afex)
library(tidyverse) 
library(dplyr)
library(readxl)
library(ggplot2)
library(lme4) 
library(lmerTest)
library(readr)
library(maditr)
library(patchwork)
library(janitor)
library(openxlsx)
library(Routliers)
library(lsmeans)
library(Hmisc)
library(car)
library(MPsychoR)
library(eigenmodel)
library(rmcorr)

options(scipen = 999) # Remove scientific notation
`%notin%` <- Negate(`%in%`) # Define %notin% function
```

Load data (all .xlsx files)

```{r}
# Specify the path accordingly
xlsx_files <- list.files(path='pilot-1/data', pattern="*.xlsx", full.names=TRUE)

# Specify names of the dataframes 
names_xlsx <- sub('.*\\/', '', xlsx_files)
names_xlsx <- substr(names_xlsx, 1, nchar(names_xlsx) - 5)

# List all files
all_xlsx <- lapply(xlsx_files, read_excel)

# Name all files
names(all_xlsx) <- names_xlsx

# Save each element in the list into a separate R object
list2env(all_xlsx, envir=.GlobalEnv)
```

Data cleaning

```{r}
# Rename dataframes
additionalGoals <- `pilot-1-additional-goals`
consent <- `pilot-1-consent`
demographics <- `pilot-1-demographics`
experimentDetails <- `pilot-1-experiment-details`
politicalIdeology <- `pilot-1-political-ideology`
politicalParty <- `pilot-1-political-party`
taskConLibSelf <- `pilot-1-task-con-lib-self`
taskConSelfLib <- `pilot-1-task-con-self-lib`
taskLibConSelf <- `pilot-1-task-lib-con-self`
taskLibSelfCon <- `pilot-1-task-lib-self-con`
taskSelfConLib <- `pilot-1-task-self-con-lib`
taskSelfLibCon <- `pilot-1-task-self-lib-con`
technicalDifficulties <- `pilot-1-technical-difficulties`

# Clean task data
taskCombined <- bind_rows(taskConLibSelf, taskConSelfLib, taskLibConSelf, taskLibSelfCon, taskSelfConLib, taskSelfLibCon)

taskCombined <- taskCombined[, c('participantID', 'taskRandomiser', 'Trial Number', 'Zone Name', 'Zone Type', 'Reaction Time', 'Response', 'display', 'sliderText')]

# Rename columns to manipulate them easier
names(taskCombined)[3] <- 'trialNumber'
names(taskCombined)[4] <- 'zoneName'
names(taskCombined)[5] <- 'zoneType'
names(taskCombined)[6] <- 'reactionTime'
names(taskCombined)[7] <- 'response'

taskCombined <- taskCombined %>%
  dplyr::filter(display != 'instructions' & zoneType == 'response_slider_endValue')

# Cleaned task data
taskFinal <- taskCombined[, c('participantID', 'taskRandomiser', 'trialNumber', 'zoneName', 'reactionTime', 'response', 'sliderText')]

names(taskFinal)[4] <- 'perspective'
names(taskFinal)[7] <- 'policyGoal'

# Clean political ideology
politicalIdeologyFinal <- politicalIdeology %>%
  dplyr::filter(politicalIdeology$`Zone Type` == 'response_slider_endValue')

politicalIdeologyFinal <- politicalIdeologyFinal[, c('participantID', 'Zone Name', 'Response')]

# Cleaned political ideology
politicalIdeologyFinal <- dcast(politicalIdeologyFinal,
                                participantID ~ `Zone Name`,
                                value.var = 'Response')

# Combine all datasets
pilot1Data <- left_join(demographics, taskFinal, by = c('participantID', 'taskRandomiser'))
pilot1Data <- left_join(pilot1Data, additionalGoals, by = "participantID")
pilot1Data <- left_join(pilot1Data, politicalParty, by = "participantID")
pilot1Data <- left_join(pilot1Data, politicalIdeologyFinal, by = "participantID")
pilot1Data <- left_join(pilot1Data, technicalDifficulties, by = "participantID")

# Export data into a .csv file
write.csv(pilot1Data, 'pilot1Data.csv')
```

Data analysis

Steps:

1. Operationalise political affiliation
  1a. Average economic and social views
  1b. Use the approach from Zmigrod et al. (2018)
  
2. Calculate actual disagreement between conservative and liberal participants 
3. Calculate perceived disagreement between conservative and liberal participants (difference scores within each participant)

```{r}

```

