---
title: "JRP Pilot 1 (UK data)"
author: "Jelka Stojanov"
date: "10/02/2022"
output: html_document
---

Load packages

```{r}
library(interactions)
library(afex)
library(tidyverse) 
library(dplyr)
library(readxl)
library(ggplot2)
library(lme4) 
library(lmerTest)
library(readr)
library(maditr)
library(patchwork)
library(janitor)
library(openxlsx)
library(Routliers)
library(lsmeans)
library(Hmisc)
library(car)
library(MPsychoR)
library(eigenmodel)
library(rmcorr)

options(scipen = 999) # Remove scientific notation
`%notin%` <- Negate(`%in%`) # Define %notin% function
```

Load data (all .xlsx files)

```{r}
# Specify the path accordingly
xlsx_files <- list.files(path='pilot-1/data', pattern="*.xlsx", full.names=TRUE)

# Specify names of the dataframes 
names_xlsx <- sub('.*\\/', '', xlsx_files)
names_xlsx <- substr(names_xlsx, 1, nchar(names_xlsx) - 5)

# List all files
all_xlsx <- lapply(xlsx_files, read_excel)

# Name all files
names(all_xlsx) <- names_xlsx

# Save each element in the list into a separate R object
list2env(all_xlsx, envir=.GlobalEnv)
```

Data cleaning

```{r}
# Rename dataframes
additionalGoals <- `pilot-1-additional-goals`
consent <- `pilot-1-consent`
demographics <- `pilot-1-demographics`
experimentDetails <- `pilot-1-experiment-details`
politicalIdeology <- `pilot-1-political-ideology`
politicalParty <- `pilot-1-political-party`
taskConLibSelf <- `pilot-1-task-con-lib-self`
taskConSelfLib <- `pilot-1-task-con-self-lib`
taskLibConSelf <- `pilot-1-task-lib-con-self`
taskLibSelfCon <- `pilot-1-task-lib-self-con`
taskSelfConLib <- `pilot-1-task-self-con-lib`
taskSelfLibCon <- `pilot-1-task-self-lib-con`
technicalDifficulties <- `pilot-1-technical-difficulties`

# Clean task data
taskCombined <- bind_rows(taskConLibSelf, taskConSelfLib, taskLibConSelf, taskLibSelfCon, taskSelfConLib, taskSelfLibCon)

taskCombined <- taskCombined[, c('participantID', 'taskRandomiser', 'Trial Number', 'Zone Name', 'Zone Type', 'Reaction Time', 'Response', 'display', 'sliderText')]

# Rename columns to manipulate them easier
names(taskCombined)[3] <- 'trialNumber'
names(taskCombined)[4] <- 'zoneName'
names(taskCombined)[5] <- 'zoneType'
names(taskCombined)[6] <- 'reactionTime'
names(taskCombined)[7] <- 'response'

taskCombined <- taskCombined %>%
  dplyr::filter(display != 'instructions' & zoneType == 'response_slider_endValue')

# Cleaned task data
taskFinal <- taskCombined[, c('participantID', 'taskRandomiser', 'trialNumber', 'zoneName', 'reactionTime', 'response', 'sliderText')]

names(taskFinal)[4] <- 'perspective'
names(taskFinal)[7] <- 'policyGoal'

# Clean political ideology
politicalIdeologyFinal <- politicalIdeology %>%
  dplyr::filter(politicalIdeology$`Zone Type` == 'response_slider_endValue')

politicalIdeologyFinal <- politicalIdeologyFinal[, c('participantID', 'Zone Name', 'Response')]

# Cleaned political ideology
politicalIdeologyFinal <- dcast(politicalIdeologyFinal,
                                participantID ~ `Zone Name`,
                                value.var = 'Response')

# Combine all datasets
pilot1Data <- left_join(demographics, taskFinal, by = c('participantID', 'taskRandomiser'))
pilot1Data <- left_join(pilot1Data, additionalGoals, by = "participantID")
pilot1Data <- left_join(pilot1Data, politicalParty, by = "participantID")
pilot1Data <- left_join(pilot1Data, politicalIdeologyFinal, by = "participantID")
pilot1Data <- left_join(pilot1Data, technicalDifficulties, by = "participantID")

# Export data into a .csv file
write.csv(pilot1Data, 'pilot1Data.csv')
```

#########

DATA ANALYSIS

########

TASK 1: All 7 of us should go through the policy goals included in Pilot 1 (SLO/UK) and categorise them as economic/social in different pages of the Excel sheet.


TASK 2 (Analysis steps):

1. Categorise people based on political affiliation
  1a. Average economic and social views and classify those over 50 as conservative, those below 50 as liberal
  1b. Use economic and social views separately for economic and social goals (Same classification logic)
  1c. Use the approach from Zmigrod et al. (2018) - Scores for each political party can be found in the Supplementary materials. Some political parties might not have scores so look for alternative YouGov data.
  
2. Calculate actual disagreement between conservative and liberal participants - For this part, exclude strict moderates (those who scored 50).
3. Calculate perceived disagreement between conservative and liberal participants (first calculate the difference scores within each participant and then average them) - Strict moderates should be included at first, but when we are doing the comparison between liberal and conservative samples, they should be exluded again (since they don't strictly fall into any of the political categories).

```{r}
cor.test(politicalIdeologyFinal$economiclViews, politicalIdeologyFinal$socialViews) # How correlated are economic and social views?

# Approach 1a
politicalIdeologyFinal$averageIdeology <- (politicalIdeologyFinal$economiclViews + politicalIdeologyFinal$socialViews) / 2

# Create a histogram
politicalIdeologyFinal %>%
  ggplot(aes(x = averageIdeology)) +
  geom_histogram()

# How many people scored 50 on different political ideology variables?
politicalIdeologyFinal %>%
  dplyr::filter(averageIdeology == 50)

politicalIdeologyFinal %>%
  dplyr::filter(economiclViews == 50)

politicalIdeologyFinal %>%
  dplyr::filter(socialViews == 50)

# Classification based on average scores
politicalIdeologyFinal$politicalAffiliationGroup <- 
  if_else(politicalIdeologyFinal$averageIdeology > 50, 'Conservative', 
  if_else(politicalIdeologyFinal$averageIdeology < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinal$politicalAffiliationGroup)

# Classification based on economic views
politicalIdeologyFinal$economicGroup <- 
  if_else(politicalIdeologyFinal$economiclViews > 50, 'Conservative', 
  if_else(politicalIdeologyFinal$economiclViews < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinal$economicGroup)

# Classification based on social views
politicalIdeologyFinal$socialGroup <- 
  if_else(politicalIdeologyFinal$socialViews > 50, 'Conservative', 
  if_else(politicalIdeologyFinal$socialViews < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinal$socialGroup)

# Summary stats that you care about the most
# You can save grouped summary stats into an object and export it using write.csv() function
X <- pilot1Data %>% # Remember that you don't currently have political affiliation columns in this dataset (pilot1Data)!
  dlyr::filter(politicalAffiliationGroup != 'Moderate') %>%
  dplyr::group_by(policyGoal, perspective) %>% # Group by politicalAffiliationGroup later as well
  summarise(meanApproval = mean(response), medianApproval = median(response), sdApproval = sd(response), madApproval = mad(response))

# Specify the score for each party - Approach 1c
pilot1Data$politicalPartyScore <- 
  if_else(pilot1Data$politicalParty == 'Labour', 3.2, 999) # Add other political parties here
```



