---
title: "Pilot 1 (Political issues) - Cleaning & analysis code"
output: html_document
date: '2023-02-23'
---

Load packages

```{r}
library(afex)
library(bootnet)
library(car)
library(dplyr)
library(eigenmodel)
library(ggplot2)
library(glasso)
library(Hmisc)
library(interactions)
library(janitor)
library(lmerTest)
library(lme4) 
library(lsmeans)
library(maditr)
library(MPsychoR)
library(NetworkComparisonTest)
library(networktools)
library(openxlsx)
library(patchwork)
library(ppcor)
library(qgraph)
library(readr)
library(readxl)
library(rmcorr)
library(Routliers)
library(simr)
library(tidyverse) 

# Remove scientific notation
options(scipen = 999) 

# Define %notin% function
`%notin%` <- Negate(`%in%`) 
```

################## UK ##################

#########

DATA LOADING

########

```{r}
# Specify the path accordingly
xlsx_files <- list.files(path='UK/Raw data', pattern="*.xlsx", full.names=TRUE)

# Specify names of the dataframes 
names_xlsx <- sub('.*\\/', '', xlsx_files)
names_xlsx <- substr(names_xlsx, 1, nchar(names_xlsx) - 5)

# List all files
all_xlsx <- lapply(xlsx_files, read_excel)

# Name all files
names(all_xlsx) <- names_xlsx

# Save each element in the list into a separate R object
list2env(all_xlsx, envir=.GlobalEnv)
```

#########

DATA CLEANING

########

```{r}
# Rename dataframes
additionalGoals <- `pilot-1-additional-goals`
consent <- `pilot-1-consent`
demographics <- `pilot-1-demographics`
experimentDetails <- `pilot-1-experiment-details`
politicalIdeology <- `pilot-1-political-ideology`
politicalParty <- `pilot-1-political-party`
taskConLibSelf <- `pilot-1-task-con-lib-self`
taskConSelfLib <- `pilot-1-task-con-self-lib`
taskLibConSelf <- `pilot-1-task-lib-con-self`
taskLibSelfCon <- `pilot-1-task-lib-self-con`
taskSelfConLib <- `pilot-1-task-self-con-lib`
taskSelfLibCon <- `pilot-1-task-self-lib-con`
technicalDifficulties <- `pilot-1-technical-difficulties`

# Clean task data
taskCombined <- bind_rows(taskConLibSelf, taskConSelfLib, taskLibConSelf, taskLibSelfCon, taskSelfConLib, taskSelfLibCon)

taskCombined <- taskCombined[, c('participantID', 'taskRandomiser', 'Trial Number', 'Zone Name', 'Zone Type', 'Reaction Time', 'Response', 'display', 'sliderText')]

# Rename columns to manipulate them easier
names(taskCombined)[3] <- 'trialNumber'
names(taskCombined)[4] <- 'zoneName'
names(taskCombined)[5] <- 'zoneType'
names(taskCombined)[6] <- 'reactionTime'
names(taskCombined)[7] <- 'response'

taskCombined <- taskCombined %>%
  dplyr::filter(display != 'instructions' & zoneType == 'response_slider_endValue')

# Cleaned task data
taskFinal <- taskCombined[, c('participantID', 'taskRandomiser', 'trialNumber', 'zoneName', 'reactionTime', 'response', 'sliderText')]

names(taskFinal)[4] <- 'perspective'
names(taskFinal)[7] <- 'policyGoal'

# Clean political ideology
politicalIdeologyFinal <- politicalIdeology %>%
  dplyr::filter(politicalIdeology$`Zone Type` == 'response_slider_endValue')

politicalIdeologyFinal <- politicalIdeologyFinal[, c('participantID', 'Zone Name', 'Response')]

# Cleaned political ideology
politicalIdeologyFinal <- dcast(politicalIdeologyFinal,
                                participantID ~ `Zone Name`,
                                value.var = 'Response')

# Combine all datasets
pilot1Data <- left_join(demographics, taskFinal, by = c('participantID', 'taskRandomiser'))
pilot1Data <- left_join(pilot1Data, additionalGoals, by = "participantID")
pilot1Data <- left_join(pilot1Data, politicalParty, by = "participantID")
pilot1Data <- left_join(pilot1Data, politicalIdeologyFinal, by = "participantID")
pilot1Data <- left_join(pilot1Data, technicalDifficulties, by = "participantID")
```

#########

DATA ANALYSIS

########

TASK 1: All 7 of us should go through the policy goals included in Pilot 1 (SLO/UK) and categorise them as economic/social in different pages of the Excel sheet.

TASK 2 (Analysis steps):

1. Categorise people based on political affiliation
  1a. Average economic and social views and classify those over 50 as conservative, those below 50 as liberal.
  1b. Use economic and social views separately for economic and social goals (Same classification logic).
  1c. Use the approach from Zmigrod et al. (2018) - Scores for each political party can be found in the Supplementary materials. Some political parties might not have scores so look for alternative YouGov data.
  
2. Calculate actual disagreement between conservative and liberal participants - For this part, exclude strict moderates (those who scored 50).
3. Calculate perceived disagreement between conservative and liberal participants (first calculate the difference scores within each participant and then calculate the descriptive stats of these difference scores). Strict moderates should be included at first, but when we are doing the comparison between liberal and conservative samples, they should be exluded again (since they don't strictly fall into any of the political categories).

```{r}
# INITIAL EXAMINATION OF THE DATA
cor.test(politicalIdeologyFinal$economiclViews, politicalIdeologyFinal$socialViews) # How correlated are economic and social views?

# Approach 1a
politicalIdeologyFinal$averageIdeology <- (politicalIdeologyFinal$economiclViews + politicalIdeologyFinal$socialViews) / 2

# Create a histogram
politicalIdeologyFinal %>%
  ggplot(aes(x = averageIdeology)) +
  geom_histogram()

# How many people scored 50 on different political ideology variables?
politicalIdeologyFinal %>%
  dplyr::filter(averageIdeology == 50)

politicalIdeologyFinal %>%
  dplyr::filter(economiclViews == 50)

politicalIdeologyFinal %>%
  dplyr::filter(socialViews == 50)

# Classification based on average scores FOR COUNTING PURPOSES
politicalIdeologyFinal$politicalAffiliationGroup <- 
  if_else(politicalIdeologyFinal$averageIdeology > 50, 'Conservative', 
  if_else(politicalIdeologyFinal$averageIdeology < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinal$politicalAffiliationGroup)

# Classification based on economic views
politicalIdeologyFinal$economicGroup <- 
  if_else(politicalIdeologyFinal$economiclViews > 50, 'Conservative', 
  if_else(politicalIdeologyFinal$economiclViews < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinal$economicGroup)

# Classification based on social views
politicalIdeologyFinal$socialGroup <- 
  if_else(politicalIdeologyFinal$socialViews > 50, 'Conservative', 
  if_else(politicalIdeologyFinal$socialViews < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinal$socialGroup)

# Categorisation of participants and policy goals ON TASK DATA

# Average political ideology
pilot1Data$politicalIdeology <- (pilot1Data$economiclViews + pilot1Data$socialViews) / 2

# Scores based on Zmigrod et al. (2018)

# These calculations provided the following conservatism scores for each political party: UKIP (+2.27), Conservative Party (+1.55), Liberal Democrats (−0.64), Plaid Cymru (−1.00), Scottish National Party (−1.75), Labour Party (−2.5), and Green Party (−5.5).
unique(pilot1Data$politicalParty)

table(pilot1Data$politicalConservatismScore)

pilot1Data$politicalConservatismScore <- 
  ifelse(pilot1Data$politicalParty %in% c('Labour', 'Voted Conservative, actually Labour'), -2.5, 
  ifelse(pilot1Data$politicalParty %in% c('Conservative', 'Republican party'), 1.55, 
  ifelse(pilot1Data$politicalParty %in% c('UKIP', 'BUF'), 2.27,
  ifelse(pilot1Data$politicalParty == 'Green', -5.5,
  ifelse(pilot1Data$politicalParty == 'Scottish National Party', -1.75,
  ifelse(pilot1Data$politicalParty == 'Liberal Democrats', -0.64, 'No score'))))))

# Categorisation of policy goals
pilot1Data$policyGoalCategory <- if_else(pilot1Data$policyGoal %in% 
  c("Higher income for minimum wage workers", "Helping wealthy individuals obtain tax benefits", "Helping major corporations obtain tax benefits", "Reducing carbon pollution", "Increasing public funding for the National Health Service (NHS)", "Having a more privatised healthcare", "Supporting British (as opposed to international) businesses and products", "Strengthening trade unions (Trade unions are organisations with members who are usually workers or employees, and trade unions look after workers' rights and interests.)", "Supporting free market economy with little government interference", "Increasing donations to UK-based charities working on issues within the UK as opposed to international charities", "Increasing people’s support for a universal basic income pilot (Universal basic income is a regular payment that is given to everyone in society to create a minimum income floor.)", "Reducing the financial strain on low-income earners and families", "Preventing borrowers from becoming over-indebted", "Ensuring people save enough money for retirement", "Increasing the circle of beneficiaries of Universal Credit (Universal Credit is a payment to help with your living costs.)"), "Economic", "Social")

pilot1Data$politicalIdeologyGroups <- 
  if_else(pilot1Data$politicalIdeology > 50, 'Conservative',
  if_else(pilot1Data$politicalIdeology < 50, 'Liberal', 'Moderate'))

table(pilot1Data$politicalIdeologyGroups)

pilot1Data$economicViewsGroups <- 
  if_else(pilot1Data$economiclViews > 50, 'Conservative',
  if_else(pilot1Data$economiclViews < 50, 'Liberal', 'Moderate'))

table(pilot1Data$economicViewsGroups)

pilot1Data$socialViewsGroups <- 
  if_else(pilot1Data$socialViews > 50, 'Conservative',
  if_else(pilot1Data$socialViews < 50, 'Liberal', 'Moderate'))

table(pilot1Data$socialViewsGroups)

pilot1Data$conservatismScoreGroups <- 
  if_else(pilot1Data$politicalConservatismScore %in% c("1.55", "2.27"), 'Conservative',
  if_else(pilot1Data$politicalConservatismScore %in% c("-5.5", "-2.5", "-1.75", "-0.64"), 'Liberal',
  if_else(pilot1Data$politicalConservatismScore == 'No score', 'Not classified', 'Mistake')))

table(pilot1Data$conservatismScoreGroups)

# Data split by perspective
pilot1DataSelf <- pilot1Data %>%
  dplyr::filter(perspective == 'selfOpinion')

pilot1DataPerceived <- pilot1Data %>%
  dplyr::filter(perspective %in% c('liberalOpinion', 'conservativeOpinion'))
```

#########

FIRST APPROACH - AVERAGE AFFILIATION

########

```{r}
# First approach

# Self
summaryPoliticalIdeologyGroupsSelf <- pilot1DataSelf %>% 
  dplyr::group_by(politicalIdeologyGroups, policyGoal) %>%
  dplyr::summarise(meanSupport  = mean(response), sdSupport = sd(response), medianSupport = median(response), madSupport = mad(response))

summaryPoliticalIdeologyGroupsSelfDcast <- dcast(summaryPoliticalIdeologyGroupsSelf, 
                                        policyGoal ~ politicalIdeologyGroups, 
                                        value.var = c('meanSupport', 'medianSupport', 'sdSupport', 'madSupport'))

summaryPoliticalIdeologyGroupsSelfDcast$actualDifference_M <- summaryPoliticalIdeologyGroupsSelfDcast$meanSupport_Liberal - summaryPoliticalIdeologyGroupsSelfDcast$meanSupport_Conservative

summaryPoliticalIdeologyGroupsSelfDcast$actualDifference_MDN <- summaryPoliticalIdeologyGroupsSelfDcast$medianSupport_Liberal - summaryPoliticalIdeologyGroupsSelfDcast$medianSupport_Conservative

write.csv(summaryPoliticalIdeologyGroupsSelfDcast, 'summaryPoliticalIdeologyGroups_Actual.csv')

# Perceived
pilot1DataPerceived <- pilot1Data %>%
  dplyr::filter(perspective %in% c('liberalOpinion', 'conservativeOpinion'))

pilot1DataPerceivedDcast <- dcast(pilot1DataPerceived, 
                                        participantID + policyGoal ~ perspective, 
                                        value.var = 'response')

pilot1DataPerceivedDcast$perceivedDifference <- pilot1DataPerceivedDcast$liberalOpinion - pilot1DataPerceivedDcast$conservativeOpinion

summaryPoliticalIdeologyGroupsPerceived <- pilot1DataPerceivedDcast %>% 
  dplyr::group_by(policyGoal) %>%
  dplyr::summarise(meanPerceivedDifference  = mean(perceivedDifference), medianPerceivedDifference = median(perceivedDifference), sdPerceivedDifference = sd(perceivedDifference), madPerceivedDifference = mad(perceivedDifference), meanConservative = mean(conservativeOpinion), medianConservative = median(conservativeOpinion), sdConservative = sd(conservativeOpinion), madConservative = mad(conservativeOpinion), meanLiberal = mean(liberalOpinion), medianLiberal = median(liberalOpinion), sdLiberal = sd(liberalOpinion), madLiberal = mad(liberalOpinion))

write.csv(summaryPoliticalIdeologyGroupsPerceived, 'summaryPoliticalIdeologyGroups_Perceived.csv')
```

#########

SECOND APPROACH - SEPARATE ECONOMIC AND SOCIAL VIEWS

########

```{r}
# Self

# Economic goals
summaryEconomicGroupsSelf <- pilot1DataSelf %>% 
  dplyr::filter(policyGoalCategory == 'Economic') %>%
  dplyr::group_by(economicViewsGroups, policyGoal) %>%
  dplyr::summarise(meanSupport  = mean(response), sdSupport = sd(response), medianSupport = median(response), madSupport = mad(response))

summaryEconomicGroupsSelfDcast <- dcast(summaryEconomicGroupsSelf, 
                                        policyGoal ~ economicViewsGroups, 
                                        value.var = c('meanSupport', 'medianSupport', 'sdSupport', 'madSupport'))

summaryEconomicGroupsSelfDcast$actualDifference_M <- summaryEconomicGroupsSelfDcast$meanSupport_Liberal - summaryEconomicGroupsSelfDcast$meanSupport_Conservative

summaryEconomicGroupsSelfDcast$actualDifference_MDN <- summaryEconomicGroupsSelfDcast$medianSupport_Liberal - summaryEconomicGroupsSelfDcast$medianSupport_Conservative

# Social goals
summarySocialGroupsSelf <- pilot1DataSelf %>% 
  dplyr::filter(policyGoalCategory == 'Social') %>%
  dplyr::group_by(socialViewsGroups, policyGoal) %>%
  dplyr::summarise(meanSupport  = mean(response), sdSupport = sd(response), medianSupport = median(response), madSupport = mad(response))

summarySocialGroupsSelfDcast <- dcast(summarySocialGroupsSelf, 
                                        policyGoal ~ socialViewsGroups, 
                                        value.var = c('meanSupport', 'medianSupport', 'sdSupport', 'madSupport'))

summarySocialGroupsSelfDcast$actualDifference_M <- summarySocialGroupsSelfDcast$meanSupport_Liberal - summarySocialGroupsSelfDcast$meanSupport_Conservative

summarySocialGroupsSelfDcast$actualDifference_MDN <- summarySocialGroupsSelfDcast$medianSupport_Liberal - summarySocialGroupsSelfDcast$medianSupport_Conservative

summarySocialEconomicGroupsSelfDcast <- bind_rows(summaryEconomicGroupsSelfDcast, summarySocialGroupsSelfDcast)

write.csv(summarySocialEconomicGroupsSelfDcast, 'summarySocialEconomicGroups_Actual.csv')

# Perceived file will be the same as for the first approach.
```

#########

THIRD APPROACH - SCORES

########

```{r}
# Self
table(pilot1DataSelf$conservatismScoreGroups)
table(summaryConservatismScoreGroupsSelf$conservatismScoreGroups)

summaryConservatismScoreGroupsSelf <- pilot1DataSelf %>% 
  dplyr::group_by(conservatismScoreGroups, policyGoal) %>%
  dplyr::summarise(meanSupport  = mean(response), sdSupport = sd(response), medianSupport = median(response), madSupport = mad(response))

summaryConservatismScoreGroupsSelfDcast <- dcast(summaryConservatismScoreGroupsSelf, 
                                        policyGoal ~ conservatismScoreGroups, 
                                        value.var = c('meanSupport', 'medianSupport', 'sdSupport', 'madSupport'))

summaryConservatismScoreGroupsSelfDcast$actualDifference_M <- summaryConservatismScoreGroupsSelfDcast$meanSupport_Liberal - summaryConservatismScoreGroupsSelfDcast$meanSupport_Conservative

summaryConservatismScoreGroupsSelfDcast$actualDifference_MDN <- summaryConservatismScoreGroupsSelfDcast$medianSupport_Liberal - summaryConservatismScoreGroupsSelfDcast$medianSupport_Conservative

write.csv(summaryConservatismScoreGroupsSelfDcast, 'summaryConservatismScoreGroups_Actual.csv')
```

#########

PCA

########

```{r}
install.packages('factoextra')
library(factoextra)

PCASelf <- select(pilot1DataSelf, c(participantID, policyGoal, response))

PCASelf <- dcast(PCASelf,
                 participantID ~ policyGoal,
                 value.var = 'response')

PCASelfAnonymous <- select(PCASelf, -participantID)

# Rename columns - With participantID
names(PCASelf) <- c('participantID', 'intergrationEnglishSkills', 'politicalCorrectness', 'STDs', 'lowerImmigration', 'speedLimit', 'military', 'retirement', 'hormoneTherapy', 'firstJobSearch', 'adoptionSingleParent', 'adopSameSexCou', 'immEveryone', 'immHighSkill', 'LGBTQlanguage', 'privateHealth', 'corportationTax', 'wealthTax', 'minimumWage', 'financialLiteracy', 'fertilitySameSex', 'firearms', 'UKdonations', 'UBI', 'publicNHS', 'contraception', 'sustainableTransport', 'universalCredit', 'covidVacc', 'childVacc', 'policePower', 'culturalClothes', 'highEduAfford', 'dismissEmployees', 'mentalHealth', 'overIndebted', 'STEM', 'animalWelfare', 'sharedParLeave', 'abortion', 'carbonPoll', 'crimePunishment', 'homelessness', 'publicSmoking', 'strainLIFamilies', 'energyConsumption', 'minorityBackground', 'tradeUnions', 'britishProducts', 'freeMarket', 'countryBorder', 'policeControl')

write.csv(PCASelf, 'PCASelf.csv')

# Rename columns - Without participantID
names(PCASelfAnonymous) <- c('intergrationEnglishSkills', 'politicalCorrectness', 'STDs', 'lowerImmigration', 'speedLimit', 'military', 'retirement', 'hormoneTherapy', 'firstJobSearch', 'adoptionSingleParent', 'adopSameSexCou', 'immEveryone', 'immHighSkill', 'LGBTQlanguage', 'privateHealth', 'corportationTax', 'wealthTax', 'minimumWage', 'financialLiteracy', 'fertilitySameSex', 'firearms', 'UKdonations', 'UBI', 'publicNHS', 'contraception', 'sustainableTransport', 'universalCredit', 'covidVacc', 'childVacc', 'policePower', 'culturalClothes', 'highEduAfford', 'dismissEmployees', 'mentalHealth', 'overIndebted', 'STEM', 'animalWelfare', 'sharedParLeave', 'abortion', 'carbonPoll', 'crimePunishment', 'homelessness', 'publicSmoking', 'strainLIFamilies', 'energyConsumption', 'minorityBackground', 'tradeUnions', 'britishProducts', 'freeMarket', 'countryBorder', 'policeControl')
                  
resPCA <- prcomp(PCASelfAnonymous, scale = TRUE)
fviz_eig(resPCA)
print(resPCA)

# Add economic/social views
PCASelfIdeology <- select(pilot1DataSelf, c(participantID, economicViews, socialViews, policyGoal, response))

PCASelfIdeology <- dcast(PCASelfIdeology,
                 participantID + economicViews + socialViews ~ policyGoal,
                 value.var = 'response')

names(PCASelfIdeology) <- c('participantID', 'economicViews', 'socialViews', 'intergrationEnglishSkills', 'politicalCorrectness', 'STDs', 'lowerImmigration', 'speedLimit', 'military', 'retirement', 'hormoneTherapy', 'firstJobSearch', 'adoptionSingleParent', 'adopSameSexCou', 'immEveryone', 'immHighSkill', 'LGBTQlanguage', 'privateHealth', 'corportationTax', 'wealthTax', 'minimumWage', 'financialLiteracy', 'fertilitySameSex', 'firearms', 'UKdonations', 'UBI', 'publicNHS', 'contraception', 'sustainableTransport', 'universalCredit', 'covidVacc', 'childVacc', 'policePower', 'culturalClothes', 'highEduAfford', 'dismissEmployees', 'mentalHealth', 'overIndebted', 'STEM', 'animalWelfare', 'sharedParLeave', 'abortion', 'carbonPoll', 'crimePunishment', 'homelessness', 'publicSmoking', 'strainLIFamilies', 'energyConsumption', 'minorityBackground', 'tradeUnions', 'britishProducts', 'freeMarket', 'countryBorder', 'policeControl')

PCASelfIdeology$participantID <- NULL

library(ppcor)
cor(PCASelfIdeology)
```

################## SLO ##################

#########

DATA LOADING

########

```{r}
# Specify the path accordingly
csv_files <- list.files(path='SLO/Raw data', pattern="*.csv", full.names=TRUE)

# Specify names of the dataframes 
names_csv <- sub('.*\\/', '', csv_files)
names_csv <- substr(names_csv, 1, nchar(names_csv) - 4)

# List all files
all_csv <- lapply(csv_files, read_csv)

# Name all files
names(all_csv) <- names_csv

# Save each element in the list into a separate R object
list2env(all_csv, envir = .GlobalEnv)
```

#########

DATA CLEANING

########

```{r}
# Rename dataframes
additionalGoalsSlo <- `pilot-1-additional-goals-slo`
consentSlo <- `pilot-1-consent-slo`
demographicsSlo <- `pilot-1-demographics-slo`
experimentDetailsSlo <- `pilot-1-experiment-details-slo`
politicalIdeologySlo <- `pilot-1-political-ideology-slo`
politicalPartySlo <- `pilot-1-political-party-slo`
taskConLibSelfSlo <- `pilot-1-task-con-lib-self-slo`
taskConSelfLibSlo <- `pilot-1-task-con-self-lib-slo`
taskLibConSelfSlo <- `pilot-1-task-lib-con-self-slo`
taskLibSelfConSlo <- `pilot-1-task-lib-self-con-slo`
taskSelfConLibSlo <- `pilot-1-task-self-con-lib-slo`
taskSelfLibConSlo <- `pilot-1-task-self-lib-con-slo`
liberarianismSlo <- `pilot-1-libertarianism-slo`
technicalDifficultiesSlo <- `pilot-1-technical-difficulties-slo`

taskCombinedSlo <- bind_rows(taskConLibSelfSlo, taskConSelfLibSlo, taskLibConSelfSlo, taskLibSelfConSlo, taskSelfConLibSlo, taskSelfLibConSlo)

taskCombinedSlo <- taskCombinedSlo[, c('participantID', 'taskRandomiser', 'Trial Number', 'Zone Name', 'Zone Type', 'Reaction Time', 'Response', 'display', 'sliderText')]

# Rename columns to manipulate them easier
names(taskCombinedSlo)[3] <- 'trialNumber'
names(taskCombinedSlo)[4] <- 'zoneName'
names(taskCombinedSlo)[5] <- 'zoneType'
names(taskCombinedSlo)[6] <- 'reactionTime'
names(taskCombinedSlo)[7] <- 'response'

taskCombinedSlo <- taskCombinedSlo %>%
  dplyr::filter(display != 'instructions' & zoneType == 'response_slider_endValue')

# Cleaned task data
taskFinalSlo <- taskCombinedSlo[, c('participantID', 'taskRandomiser', 'trialNumber', 'zoneName', 'reactionTime', 'response', 'sliderText')]

names(taskFinalSlo)[4] <- 'perspective'
names(taskFinalSlo)[7] <- 'policyGoal'

# Clean political ideology
politicalIdeologyFinalSlo <- politicalIdeologySlo %>%
  dplyr::filter(politicalIdeologySlo$`Zone Type` == 'response_slider_endValue')

politicalIdeologyFinalSlo <- politicalIdeologyFinalSlo[, c('participantID', 'Zone Name', 'Response')]

# Cleaned political ideology
politicalIdeologyFinalSlo <- dcast(politicalIdeologyFinalSlo,
                                participantID ~ `Zone Name`,
                                value.var = 'Response')

# Combine all datasets
pilot1DataSlo <- left_join(demographicsSlo, taskFinalSlo, by = 'participantID')
pilot1DataSlo <- left_join(pilot1DataSlo, additionalGoalsSlo, by = "participantID")
pilot1DataSlo <- left_join(pilot1DataSlo, politicalPartySlo, by = "participantID")
pilot1DataSlo <- left_join(pilot1DataSlo, politicalIdeologyFinalSlo, by = "participantID")
pilot1DataSlo <- left_join(pilot1DataSlo, liberarianismSlo, by = "participantID")
pilot1DataSlo <- left_join(pilot1DataSlo, technicalDifficultiesSlo, by = "participantID")
```

#########

DATA ANALYSIS

########

```{r}
# INITIAL EXAMINATION OF THE DATA
cor.test(politicalIdeologyFinalSlo$economiclViews, politicalIdeologyFinalSlo$socialViews) # How correlated are economic and social views? (r = .44)

# Approach 1a
politicalIdeologyFinalSlo$averageIdeology <- (politicalIdeologyFinalSlo$economiclViews + politicalIdeologyFinalSlo$socialViews) / 2

# Create a histogram
politicalIdeologyFinalSlo %>%
  ggplot(aes(x = averageIdeology)) +
  geom_histogram()

# How many people scored 50 on different political ideology variables? 

# 4
politicalIdeologyFinalSlo %>%
  dplyr::filter(averageIdeology == 50)

# 4
politicalIdeologyFinalSlo %>%
  dplyr::filter(economiclViews == 50)

# 3
politicalIdeologyFinalSlo %>%
  dplyr::filter(socialViews == 50)

# Classification based on average scores FOR COUNTING PURPOSES
politicalIdeologyFinalSlo$politicalAffiliationGroup <- 
  if_else(politicalIdeologyFinalSlo$averageIdeology > 50, 'Conservative', 
  if_else(politicalIdeologyFinalSlo$averageIdeology < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinalSlo$politicalAffiliationGroup) # 15 conservative, 29 liberal, 4 moderate

# Classification based on economic views
politicalIdeologyFinalSlo$economicGroup <- 
  if_else(politicalIdeologyFinalSlo$economiclViews > 50, 'Conservative', 
  if_else(politicalIdeologyFinalSlo$economiclViews < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinalSlo$economicGroup) # 19 conservative, 25 liberal, 4 moderate

# Classification based on social views
politicalIdeologyFinalSlo$socialGroup <- 
  if_else(politicalIdeologyFinalSlo$socialViews > 50, 'Conservative', 
  if_else(politicalIdeologyFinalSlo$socialViews < 50, 'Liberal', 'Moderate'))

table(politicalIdeologyFinalSlo$socialGroup) # 12 conservative, 33 liberal, 3 moderate

# Categorisation of participants and policy goals ON TASK DATA

# Average political ideology
pilot1DataSlo$politicalIdeology <- (pilot1DataSlo$economiclViews + pilot1DataSlo$socialViews) / 2

# Categorisation of policy goals - @ŽIGA, DO THIS SINCE THEY ARE IN SLOVENIAN.
# pilot1DataSlo$policyGoalCategory <- if_else(pilot1DataSlo$policyGoal %in% c("Higher income for minimum wage workers", "Helping wealthy individuals obtain tax benefits", "Helping major corporations obtain tax benefits", "Reducing carbon pollution", "Increasing public funding for the National Health Service (NHS)", "Having a more privatised healthcare", "Supporting British (as opposed to international) businesses and products", "Strengthening trade unions (Trade unions are organisations with members who are usually workers or employees, and trade unions look after workers' rights and interests.)", "Supporting free market economy with little government interference", "Increasing donations to UK-based charities working on issues within the UK as opposed to international charities", "Increasing people’s support for a universal basic income pilot (Universal basic income is a regular payment that is given to everyone in society to create a minimum income floor.)", "Reducing the financial strain on low-income earners and families", "Preventing borrowers from becoming over-indebted", "Ensuring people save enough money for retirement", "Increasing the circle of beneficiaries of Universal Credit (Universal Credit is a payment to help with your living costs.)"), "Economic", "Social")

pilot1DataSlo$politicalIdeologyGroups <- 
  if_else(pilot1DataSlo$politicalIdeology > 50, 'Conservative',
  if_else(pilot1DataSlo$politicalIdeology < 50, 'Liberal', 'Moderate'))

pilot1DataSlo$economicViewsGroups <- 
  if_else(pilot1DataSlo$economiclViews > 50, 'Conservative',
  if_else(pilot1DataSlo$economiclViews < 50, 'Liberal', 'Moderate'))

pilot1DataSlo$socialViewsGroups <- 
  if_else(pilot1DataSlo$socialViews > 50, 'Conservative',
  if_else(pilot1DataSlo$socialViews < 50, 'Liberal', 'Moderate'))

# Data split by perspective
pilot1DataSelfSlo <- pilot1DataSlo %>%
  dplyr::filter(perspective == 'selfOpinion')

pilot1DataPerceivedSlo <- pilot1DataSlo %>%
  dplyr::filter(perspective %in% c('liberalOpinion', 'conservativeOpinion'))
```

#########

FIRST APPROACH - AVERAGE AFFILIATION

########

```{r}
# First approach

# Self
summaryPoliticalIdeologyGroupsSelfSlo <- pilot1DataSelfSlo %>% 
  dplyr::group_by(politicalIdeologyGroups, policyGoal) %>%
  dplyr::summarise(meanSupport  = mean(response), sdSupport = sd(response), medianSupport = median(response), madSupport = mad(response))

summaryPoliticalIdeologyGroupsSelfDcastSlo <- dcast(summaryPoliticalIdeologyGroupsSelfSlo, 
                                        policyGoal ~ politicalIdeologyGroups, 
                                        value.var = c('meanSupport', 'medianSupport', 'sdSupport', 'madSupport'))

summaryPoliticalIdeologyGroupsSelfDcastSlo$actualDifference_M <- summaryPoliticalIdeologyGroupsSelfDcastSlo$meanSupport_Liberal - summaryPoliticalIdeologyGroupsSelfDcastSlo$meanSupport_Conservative

summaryPoliticalIdeologyGroupsSelfDcastSlo$actualDifference_MDN <- summaryPoliticalIdeologyGroupsSelfDcastSlo$medianSupport_Liberal - summaryPoliticalIdeologyGroupsSelfDcastSlo$medianSupport_Conservative

write.csv(summaryPoliticalIdeologyGroupsSelfDcastSlo, 'summaryPoliticalIdeologyGroups_Actual_Slo.csv')

# Perceived
pilot1DataPerceivedSlo <- pilot1DataSlo %>%
  dplyr::filter(perspective %in% c('liberalOpinion', 'conservativeOpinion'))

pilot1DataPerceivedDcastSlo <- dcast(pilot1DataPerceivedSlo, 
                                        participantID + policyGoal ~ perspective, 
                                        value.var = 'response')

pilot1DataPerceivedDcastSlo$perceivedDifference <- pilot1DataPerceivedDcastSlo$liberalOpinion - pilot1DataPerceivedDcastSlo$conservativeOpinion

summaryPoliticalIdeologyGroupsPerceivedSlo <- pilot1DataPerceivedDcastSlo %>% 
  dplyr::group_by(policyGoal) %>%
  dplyr::summarise(meanPerceivedDifference  = mean(perceivedDifference), medianPerceivedDifference = median(perceivedDifference), sdPerceivedDifference = sd(perceivedDifference), madPerceivedDifference = mad(perceivedDifference), meanConservative = mean(conservativeOpinion), medianConservative = median(conservativeOpinion), sdConservative = sd(conservativeOpinion), madConservative = mad(conservativeOpinion), meanLiberal = mean(liberalOpinion), medianLiberal = median(liberalOpinion), sdLiberal = sd(liberalOpinion), madLiberal = mad(liberalOpinion))

write.csv(summaryPoliticalIdeologyGroupsPerceivedSlo, 'summaryPoliticalIdeologyGroups_Perceived_Slo.csv')
```

#########

SECOND APPROACH - SEPARATE ECONOMIC AND SOCIAL VIEWS

########

@ŽIGA, RUN THE CODE BELOW ONCE YOU CATEGORISE THE POLICY GOALS AS ECONOMIC OR SOCIAL ABOVE.

```{r}
# Self

# Economic goals
summaryEconomicGroupsSelfSlo <- pilot1DataSelfSlo %>% 
  dplyr::filter(policyGoalCategory == 'Economic') %>%
  dplyr::group_by(economicViewsGroups, policyGoal) %>%
  dplyr::summarise(meanSupport  = mean(response), sdSupport = sd(response), medianSupport = median(response), madSupport = mad(response))

summaryEconomicGroupsSelfDcastSlo <- dcast(summaryEconomicGroupsSelfSlo, 
                                        policyGoal ~ economicViewsGroups, 
                                        value.var = c('meanSupport', 'medianSupport', 'sdSupport', 'madSupport'))

summaryEconomicGroupsSelfDcastSlo$actualDifference_M <- summaryEconomicGroupsSelfDcastSlo$meanSupport_Liberal - summaryEconomicGroupsSelfDcastSlo$meanSupport_Conservative

summaryEconomicGroupsSelfDcastSlo$actualDifference_MDN <- summaryEconomicGroupsSelfDcastSlo$medianSupport_Liberal - summaryEconomicGroupsSelfDcastSlo$medianSupport_Conservative

# Social goals
summarySocialGroupsSelfSlo <- pilot1DataSelfSlo %>% 
  dplyr::filter(policyGoalCategory == 'Social') %>%
  dplyr::group_by(socialViewsGroups, policyGoal) %>%
  dplyr::summarise(meanSupport  = mean(response), sdSupport = sd(response), medianSupport = median(response), madSupport = mad(response))

summarySocialGroupsSelfDcastSlo <- dcast(summarySocialGroupsSelfSlo, 
                                        policyGoal ~ socialViewsGroups, 
                                        value.var = c('meanSupport', 'medianSupport', 'sdSupport', 'madSupport'))

summarySocialGroupsSelfDcastSlo$actualDifference_M <- summarySocialGroupsSelfDcastSlo$meanSupport_Liberal - summarySocialGroupsSelfDcastSlo$meanSupport_Conservative

summarySocialGroupsSelfDcastSlo$actualDifference_MDN <- summarySocialGroupsSelfDcastSlo$medianSupport_Liberal - summarySocialGroupsSelfDcastSlo$medianSupport_Conservative

summarySocialEconomicGroupsSelfDcastSlo <- bind_rows(summaryEconomicGroupsSelfDcastSlo, summarySocialGroupsSelfDcastSlo)

write.csv(summarySocialEconomicGroupsSelfDcastSlo, 'summarySocialEconomicGroups_Actual_Slo.csv')

# Perceived file will be the same as for the first approach.
```